Imperative Programming with Variational Effects

### 2018-08-08 paper/paper.tex
acknowledgements

During development of the Resource DSL, we encountered a number of
difficulties in the interaction of variation and side effects. Previous variational
languages have encountered similar issues and have developed a range of
techniques to address them. This thesis builds upon this work
and provides a formal operational semantics for a simple imperative language
that includes both variation and side effects. After presenting this formalization,
we demonstrate how it is successfully applied in our work on the Resource DSL.
}
\acknowledgements{
TODO
}

>>>>

During development of the Resource DSL, we encountered a number of
difficulties in the interaction of variation and side effects. Previous variational
languages have encountered similar issues and have developed a range of
techniques to address them. This thesis builds upon this work
and provides a formal operational semantics for a simple imperative language
that includes both variation and side effects. After presenting this formalization,
we demonstrate how it is successfully applied in our work on the Resource DSL.
}
\acknowledgements{
First and foremost I want to thank my wife, Sara, without whom this certainly
would not have been possible. Thank you for supporting me while I finished
school, and especially for taking such good care of Henry and me. It's been
a long road to get here and I'm glad you were there with me. I love you and
Henry and I'm happy that with the conclusion of my studies we'll have more
time to spend together.

Special thanks to my advisor, Eric Walkingshaw, who took a chance on me
coming out of my undergraduate studies without much formal knowledge of
computer science. Your kindness and support have been invaluable during
this whole endeavor. I'm grateful for the opportunity that I've had to learn from
and collaborate with you.

A special recognition goes to Jeff Young, a great classmate and colleague, but
most importantly a true friend. I already miss our many interesting and fruitful
discussions about both computer science and everything else. Having someone
that I could bounce ideas off of and who brings an extreme level of passion and
dedication to the field has been an enormous benefit during my time here.
Similarly, I'd like to thank and recognize Mike McGirr, as a frequent participant in
these same discussions.

Thanks to all the members of the Lambda group here at Oregon State. You have
been wonderful colleagues and I've learned so much from all of you.

Thank you to the members of my program committee: Martin Erwig, Arash Termehchy,
and Adam Branscum. In particular I've had the pleasure of being in many of Martin's
excellent classes and interacting with him during our meetings as a research group.
Thank you for your excellent feedback and comments on much of my work.

I've been grateful for the tireless efforts of the membership of the Coalition of
Graduate Employees, who have successfully fought for many of the benefits that
made tackling graduate school as a young father much more achievable.

Thank you to my new employer, Marketo, for allowing me to complete and defend
my thesis and for hiring me as a fresh graduate.

Thank you to my parents, who have been constantly supportive, especially as
we moved back to Oregon. I'm glad we're staying close by, especially because Henry
loves seeing his grandparents so much. I'd also like to recognize my siblings and members of
my extended family, in particular Claudia Webb for caring for me so much during my undergraduate
studies. I love you all and am glad I have such an amazing
family.

TODO: grant
}
